Method quality control

### 2018-02-06 analysis/analyses/4-method_characterisation/2_quality_control.Rmd
small additions to method characterisation figures

Comparing qc and citations overtime     
```{r, fig.width=16, fig.height=8}
g1 <- ggplot(methods_evaluated, aes(date, qc_score)) +
    geom_smooth(span=2) +
    geom_point() +
    ggrepel::geom_label_repel(aes(label = name)) +
    cowplot::theme_cowplot() +
    labs(x = "Time", y = "QC score", title = "Code quality score over time")
g1

>>>>

Comparing qc and citations overtime     
```{r, fig.width=16, fig.height=8}
g1 <- ggplot(methods_evaluated, aes(date, qc_score)) +
    geom_smooth(span=2) +
    geom_point() +
    ggrepel::geom_label_repel(aes(label = name)) +
    cowplot::theme_cowplot() +
    labs(x = label_long("publication_date"), y = "QC score", title = "Code quality score over time")
g1
